\documentclass{article}

\begin{document}


\title{DRP Application Suggestions}

\maketitle


\section{So, you want to be accepted to participate in the DRP?}

More often than not, more students apply to the program than there are available mentors. Some of
the factors taken into consideration for participating include the number of available mentors in
your your area of interest, student seniority, and past DRP participation. These are out of your
control as a student. However, there are many things you could do as a student to improve your
chances.


\subsection{Don't give up!}

Keep applying to the DRP! Continuously applying will naturally improve your chances of selection. If
you didn't get in this semester, you are more likely to be selected for next semester. 
Priority is given to students who are older, since they have taken more math classes and will have
fewer opportunities to participate. 

\subsection{Take more math classes}

It is easier to pair students who have had more experience and exposure to different kinds of
mathematics. Since, if you know more material, there are more projects and directions you can go
into. It is a lot easier on our mentors if you have taken at least one proof-based math course.
This will be important for your success in the program.

\subsection{Tell us why you want to do DRP!}

When you apply, you will be asked to write a short paragraph about why you want to participate in
the DRP. This is your chance to tell us why you want to participate in the program. It explains how
you are interested in math research, or if you're thinking about grad school, or if you just want to
broaden your mathematical horizons. 

\end{document}

